Jane, John … Leslie? A Historical Method for Algorithmic Gender Prediction

### 2015-08-24 article.Rmd
Figures as separate files; smart quotes in Word document
Word document? WTF?

---
title: "Jane, John … Leslie? A Historical Method for Algorithmic Gender Prediction"
author: "Cameron Blevins and Lincoln Mullen"
output:
  html_document: default
  word_document: default
---

>>>>

---
title: "Jane, John … Leslie? A Historical Method for Algorithmic Gender Prediction"
author: "Cameron Blevins and Lincoln Mullen"
output:
  html_document: 
    self_contained: false
  word_document:
    pandoc_args: [
      "--smart"
    ]
---
